

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE, dev = "png")
```

This vignette offers a concise guide for using version 1.0.0 or higher of the `dtwSat` package to generate a land-use map.
The package utilizes Time-Weighted Dynamic Time Warping (TWDTW) along with a 1-Nearest Neighbor (1-NN) classifier.
The subsequent sections will walk you through the process of creating a land-use map based on a set of training samples 
and a multi-band satellite image time series.

## Reading Training Samples

First, let's read a set of training samples that come with the `dtwSat` package installation.

```{r , echo = TRUE, eval = TRUE, warning = FALSE, message = FALSE}
setwd("G:/Thesis/Thesis_data/2011")
tif_files = list.files("G:/Thesis/Thesis_data/2011", pattern = "\\.tif$", full.names = TRUE) 
tif_files
library(dtwSat)

samples <- st_read("G:/Thesis/Thesis_data/2011/L2011.gpkg")

acquisition_date <- regmatches(tif_files, regexpr("[0-9]{8}", tif_files))
acquisition_date <- as.Date(acquisition_date, format = "%Y%m%d")
print(acquisition_date)
samples
library(stars)
dc <- read_stars(tif_files,
                 proxy = FALSE,
                 along = list(time = acquisition_date),
                 RasterIO = list(bands = 1:4))

# set band names
dc <- st_set_dimensions(dc, 3, c("NDBal","NDBI", "NDVI","NDWI"))

# convert band dimension to attribute
dc <- split(dc, c("band"))

print(dc)
twdtw_model <- twdtw_knn1(x = dc,
                          y = samples,
                          cycle_length = 'year',
                          time_scale = 'day',
                          time_weight = c(steepness = 0.1, midpoint = 50),
                          formula = bands ~ s(time, k=4) )

print(twdtw_model)
plot(twdtw_model)
lu2_map <- predict(dc, model = twdtw_model)
print(lu2_map)
ggplot() +
  geom_stars(data = lu2_map) +
  theme_minimal()
write_stars(lu2_map, "lu2011_map.tif")
```

*Side note:* The date in the file name is not the true acquisition date for each pixel.
MOD13Q1 is a 16-day composite product, and the date in the file name is the first day of this 16-day period.

With the files and dates in hand, we can construct a stars satellite image time series for `dtwSat`.

